---
title: 'Assignment 9: Panel Data Models'
output: pdf_document   
name: Shannon Li 
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this assignment, I want you to work with the Fatalities data we
used in the lecture notes. Convert your data into a `pdata.frame`

```{r}
library(plm)
library(lmtest)
library(stargazer)
data(Fatalities, package='AER')
pdat <- pdata.frame(Fatalities, index=c("state","year"))                                   
```

In class, we analyzed the effect on the total number of traffic
fatalities. For this assignment, I want you to do it by age group. For
that, you need to create fatality rates by age group:

```{r}
pdat$PCfatal1517 <- with(pdat, fatal1517/pop1517*1000)
pdat$PCfatal1820 <- with(pdat, fatal1820/pop1820*1000)
pdat$PCfatal2124 <- with(pdat, fatal2124/pop2124*1000)                        
```

In order to control for all other policies, you need to include in your
model ``beertax`, `breath`, `drinkage`, `jail` and `service`. For the
other variables, add the ones you think is the most appropriate to
control for. Do not spend too much time selecting these variables. I
just want you to explain why you want to add them in your
regression. You must add at least three controls. Once your have
selected them, answer the following questions using your preferred age
group among the above three.

1- Estimate the model by OLS. Interpret the result and explain why it
is not the appropriate way to measure the effect of the policies.
```{r}
fit1 <- lm(fatal~beertax+drinkage+jail+service, Fatalities)
knitr::kable(coeftest(fit1, vcov.=vcovHC)[,])
```
This is not the right way to measure the effect of policies because there is a bunch of counter-intuitive signs. The positive beertax coefficient implies that raising the tax will result in more fatalities. Imposing a jail sentence appears to decrease fatalities, which is a positive effect, and the same goes with the coefficient Breath.


2- Estimate the model using the one-way time fixed effects
model. Interpret the results.
```{r}
fit4 <- plm(fatal~beertax+breath+drinkage+jail+service,data=pdat, effect="time")
se2 <- sqrt(diag(vcovHC(fit4)))
stargazer(fit4, se=list(se2), header=FALSE, float=FALSE, digits=4,column.labels=c("Time"), model.numbers=FALSE)
```


3- Estimate the model using the one-way individual fixed effects
model. Interpret the results.
```{r}
fit2 <- lm(fatal~beertax+breath+drinkage+jail+service,data=pdat, effect="individual")
se1 <- sqrt(diag(vcovHC(fit2)))
stargazer(fit2, se=list(se1), header=FALSE, float=FALSE, digits=4,column.labels=c("Individual"), model.numbers=FALSE)
```


4- Estimate the model using the two-way fixed effects model. Interpret
the results.
```{r}
fit5 <- plm(fatal~beertax+breath+drinkage+jail+service,data=pdat, effect="twoways")
se3 <- sqrt(diag(vcovHC(fit5)))
stargazer(fit5, se=list(se3), header=FALSE, float=FALSE, digits=4,column.labels=c("Two-ways"), model.numbers=FALSE)
```


5- Compare all your results. Which model is the most likely to be
produce a good measure of the causal effect of the policies? Explain. 
